Modelagem Automática de Escoamentos em Meios Porosos via Método dos Elementos Finitos

### 2011-10-29 Thesis/chapters/ch04/implementacao.tex
Added code highlighting format for thesis using minted. It adds some dependencies in order to compile the latex code! Mainly, that now is necessary to install pygmentize before compiling, and also that it must be run with -shel-escape to use pygmentize correctly to print the code as wished. It is necessary to think if this lack of portability is worth of... probably not! As an example, it would be much more complicated to compile this file in windows right now.

\begin{figure}
\centering
\begin{xml}
<delfine>
    <geometry>
        <mesh dimension="2" order ="1" type="gmsh">
            <filename>HomoIsoBCStruct.msh</filename>
        </mesh>
        <boundary-conditions>
            <well bctype="flux-rate(m^3/d)" function="injection" id="301">.250</well>
        </boundary-conditions>  
    </geometry>
    <physical>
        <fluid-properties>
            <water use="no">
                <viscosity model="none">1.0</viscosity>
                <density model="none">0.01</density>
            </water>
        </fluid-properties>
        <rock-properties>
            <rock-type id="1">
                <porosity compressible="no">1.0</porosity>
                <permeability type="per-domain">
                    <Kxx>0.50</Kxx>
                    <Kxy>0.0</Kxy>
                    <Kxz>0.0</Kxz>
                </permeability>
            </rock-type>
        </rock-properties>
    </physical>
    <numerical>
        <pressure-solver formulation="mixedfem" type="cg">
            <tolerance>1e-10</tolerance>
        </pressure-solver>
    </numerical>
</delfine>                            
\end{xml}
\caption{Trecho de arquivo de entrada no formato *.xml.}
\label{fig:arqxmlinput}
\end{figure}

>>>>

\begin{listing}[H]
\begin{xmlcode}
<delfine>
    <geometry>
        <mesh dimension="2" order ="1" type="gmsh">
            <filename>HomoIsoBCStruct.msh</filename>
        </mesh>
        <boundary-conditions>
            <well function="inject" id="301">.250</well>
        </boundary-conditions>  
    </geometry>
    <physical>
        <rock-properties>
            <rock-type id="1">
                <porosity>1.0</porosity>
                <permeability type="per-domain">
                    <Kxx>0.50</Kxx>
                    <Kxy>0.0</Kxy>
                    <Kxz>0.0</Kxz>
                </permeability>
            </rock-type>
        </rock-properties>
    </physical>
</delfine>                            
\end{xmlcode}
\caption{Trecho de arquivo de entrada no formato *.xml.}
\label{lst:arqxmlinput}
\end{listing}

\begin{listing}[H]
\begin{pythoncode}
def MixedFEM(self, delfineVar, parameter):
	.
	.
	.      
	# Define variational form
	a = (dot((invK/mob)*sigma, tau)
		- div(tau)*u - div(sigma)*v)*dx
	L = - f*v*dx
\end{pythoncode}
\caption{Montagem do operador diferencial elíptico via \ac{MEFM}.}
\label{lst:arqpymfem}
\end{listing}

### 2011-10-29 Thesis/tese.tex
Test of command-line svn
Primeiros resultados para o exemplo homogêneo isotrópico (referência: Tese do Rogério)
Finished Example 1 (Homogeneous Isotropic case) of Results chapter. Added in Src/Utils a function to generate nice plots of the multiple residuals files.
Primeiras correções enviadas por Prof.Paulo
Added text from cilamce 2011 paper. Still missing translation
Translation to portugues from cilamce paper
Added explanation about xml, rnc and rnv... some more could be explained about it!
Added code highlighting format for thesis using minted. It adds some dependencies in order to compile

\usepackage{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
%% Change the following pdf author attribute name to your name.
\usepackage[linkcolor=black,citecolor=black,urlcolor=black,colorlinks,pdfpagelabels,pdftitle={brunoluna-msc},pdfauthor={Bruno Gustavo Borges Luna}]{hyperref}

\address{RECIFE}

@@

\title{Aceleração de Convergência via Multigrid de Simulador de Escoamentos em Meios Porosos}
\date{JULHO/2011}

@@

\begin{dedicatory}
Dedico esta dissertação à \ldots
\end{dedicatory}

@@

\tableofcontents
\listoffigures
\listoftables
% Acronyms
%\input{chapters/extras/acronyms}
\mainmatter

%% Here you include your chapters
% \include{chapters/introduction/main}

% CHAPTER 01 - INTRODUCTION
\include{chapters/ch01/introduction}

@@

\bibliographystyle{natbib}
\addcontentsline{toc}{chapter}{Referências Bibliográficas}
%% REFERENCES
\bibliography{chapters/extras/references}

% Appendix (Uncomment for using)
%\clearpage
%\addappheadtotoc
%\appendix
%\appendixpage
%% Here you include your appendix files
%\include{chapters/appendix/a01}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PACKAGES AND CUSTOMIZATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{subfigure}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{codehighlight}
\usepackage{minted}
\usemintedstyle{tango}
\newminted{xml}{bgcolor=yellow!10, frame=single, rulecolor=\color{black!50}, label="XML"}
\newminted{python}{bgcolor=yellow!10, frame=single, rulecolor=\color{black!50}, label="Python"}
\renewcommand\listingscaption{Listagem}
%% Change the following pdf author attribute name to your name.
\usepackage[linkcolor=black,citecolor=black,urlcolor=black,colorlinks,pdfpagelabels,pdftitle={brunoluna-msc},pdfauthor={Bruno Gustavo Borges Luna}]{hyperref}
% Command added to present problem in 'theorem form'
\newtheorem{problem}{Problema}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% FRONT MATTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address{Recife}

@@

\title{Modelagem Automática de Escoamentos em Meios Porosos via Método dos Elementos Finitos}
\date{Agosto/2011}

@@

\begin{dedicatory}
Dedico à \ldots
\end{dedicatory}

@@

\tableofcontents
\listoffigures
\listoftables
% ACRONYMS
\input{chapters/extras/acronyms}
\mainmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN CHAPTERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 01 - INTRODUCTION
\include{chapters/ch01/introduction}

@@

% CHAPTER 06 - CONCLUSION
\include{chapters/ch06/conclusoes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% BACK MATTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{natbib}
\addcontentsline{toc}{chapter}{Referências Bibliográficas}
% REFERENCES
\bibliography{chapters/extras/references}

% APPENDIX
\clearpage
\appendix
% A01 - USER GUIDE
\include{chapters/appendix/a01}

% A02 - SELECTED SECTIONS OF CODE
\include{chapters/appendix/a02}
